GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Add discussion and conclusion

\begin{itemize}
    \item Articles published in English
    \item Articles published after 2010
    \item Data about GDPR fines
    \item Data about \textit{Meta Platforms, Inc.} financials
    \item Data between 2018 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2010
    \item Data that is not about GDPR fines
    \item Data that is not about \textit{Meta Platforms, Inc.} financials
    \item Data before 2018
\end{itemize}

@@

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=1.00\textwidth]{violations-by-article}
%     \caption{Number of violations by GDPR
%     article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
%     \label{fig:violations-by-article}
% \end{figure}

@@

@@

>>>>

\begin{itemize}
    \item Articles published in English
    \item Articles published after 2010
    \item Data about GDPR fines above 1 million EUR
    \item Data about \textit{Meta Platforms, Inc.} financials
    \item Data between 2018 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2010
    \item Data that is about GDPR fines below 1 million EUR
    \item Data that is not about \textit{Meta Platforms, Inc.} financials
    \item Data before 2018
\end{itemize}

@@

% \begin{figure}[H] \centering
%     \includegraphics[width=1.00\textwidth]{violations-by-article}
%     \caption{Number of violations by GDPR
%     article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
%     \label{fig:violations-by-article} \end{figure}

@@

Comparing net income and monetarial amount of GDPR fines shows little to no
signs of correlation. Since the first GDPR fine was issued in 2021 as displayed
in Figure \ref{fig:amount-of-gdpr-fines}, the net income has decreased by 46.7\%
as displayed in Figure \ref{fig:net-income}. However, this can be attributed to
other macroeconomic factors because the net income of other large technology
companies such as \textit{Amazon.com, Inc.} and \textit{Alphabet, Inc.}, has
also decreased in a similar fashion\cite{amznNetIncome,googleNetIncome}. Figure
\ref{fig:rel-fines-net-income} below shows a comparison between both figures.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{rel-fines-net-income}
    \caption{Comparison between Net Income and Monetarial Amount of GDPR Fines}
    \label{fig:rel-fines-net-income}
\end{figure}

Similarly, the revenue is not affected as well. Figure
\ref{fig:rel-fines-revenue} below shows a comparison between revenue and the
monetarial amount of GDPR fines.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{rel-fines-revenue}
    \caption{Comparison between Revenue and Monetarial Amount of GDPR Fines}
    \label{fig:rel-fines-revenue}
\end{figure}

Figure \ref{fig:stock-price} shows that the first GDPR fine might have had a
negative impact on the stock price, but subsequent more severe fines did not. In
fact, the latest record-breaking fine of \$1.2 billion shows an opposite trend
where the stock price continues to increase from \$234 to \$265 by the time this
report was written. It is worth noting that the stock price reaction might
experience a delay based on whether the fine will be imposed or not as
\textit{Meta} is arguing against the fine \cite{metaArgueFine}.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{rel-fines-stock-price}
    \caption{Comparison between Stock Price and Monetarial Amount of GDPR Fines}
    \label{fig:rel-stock-price}
\end{figure}

Likewise, the unchanged volume of shares traded signals no decrease in investor
confidence as displayed in Figure \ref{fig:volume}. Figure
\ref{fig:rel-fines-volume} below shows a comparison between the volume of shares
traded and the monetarial amount of GDPR fines.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{rel-fines-volume}
    \caption{Comparison between Stock Volume and Monetarial Amount of GDPR Fines}
    \label{fig:rel-fines-volume}
\end{figure}

The average revenue per person shows no signs of correlation with the monetarial
amount of GDPR fines as shown in Figure \ref{fig:family-revenue-per-person}.

Dividing the average revenue per person by user geography region shows that
\textit{Meta's} revenue per person in Europe is less volatile than people in the
US despite Europe having nearly twice the users compared to the United
States\cite{2023q1}. The period from 31-Mar-2022 to 31-Dec-2022 is very
different from the rest of the timeline because a \%6.45 increase in revenue in
the US was met with a \%10.77 decline in revenue in Europe. Figure
\ref{fig:rel-fines-avg-revenue-per-person-region} below shows a comparison
between the average revenue per person by user geography region and the
monetarial amount of GDPR fines.

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{rel-fines-avg-revenue-per-person-region}
    \caption{Comparison between Average Revenue per Person by User Geography Region and Monetarial Amount of GDPR Fines}
    \label{fig:rel-fines-avg-revenue-per-person-region}
\end{figure}

Figure \ref{fig:facebook-mau} and Figure \ref{fig:facebook-dau} show that the
number of daily and monthly active users in Europe has been steadily increasing
regardless of the fines imposed. It is worth noting that this increase seems to
be slowing down. Other regions show a similar trend with some showing a
shrinkage in the number of users.

@@

In summary, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
have not had a substantial impact on the company's financial performance.
Investor confidence remains intact, as evidenced by the stability of the stock
price and trading volume around the time of the fines. Furthermore, the
company's revenue and net income have not been adversely affected by these
penalties. The only noticeable change is the less volatile average revenue per
person in Europe compared to the US. Especially in the period from 31-Mar-2022
to 31-Dec-2022 where a \%6.45 increase in revenue in the US was met with a
\%10.77 decline in revenue in Europe.
